BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2013-12-10 tex/3-algorithms.tex
Add comment on 34cd000 changes.

% abs, plan
Functions in \autoref{extractionAlgo} are voluntarily abstract at this point and will be explained in detail in the remaining of this section. Section \ref{extractionrulesandstringsimilarity} defines \code{AllRules}, \code{Apply} and the \code{ScoreFunction} we use for article extraction. In section \ref{timecomplexityandlinearreformulation} we analyse the time complexity of \autoref{extractionAlgo} and give it a linear time reformulation using dynamic programing. Finally, section \ref{variationsforauthorsdatesandcomments} shows how the \code{ScoreFunction} can be adapted to extract authors, dates and comments.

@@

Properties \ref{wordorderProp} and \ref{lengthProp} are essential when we deal with cases where the blog's web feed only contains an abstract or a subset of the entire post article. \autoref{similarityTable} gives examples to illustrate how these two properties hold for the Sørensen–Dice coefficient similarity but do not for \emph{edit distance} based similarities such as the Levenshtein \cite{levenshtein1966} similarity.

>>>>

% abs, plan
Functions in \autoref{extractionAlgo} are voluntarily abstract at this point and will be explained in detail in the remaining of this section.
\hyperref[extractionrulesandstringsimilarity]{Subsection~\ref*{extractionrulesandstringsimilarity}} % Waiting for \Autoref{}...
defines \code{AllRules}, \code{Apply} and the \code{ScoreFunction} we use for article extraction. In \autoref{timecomplexityandlinearreformulation} we analyse the time complexity of \autoref{extractionAlgo} and give it\TODO{not sure about this it.} a linear time reformulation using dynamic programing. Finally, \autoref{variationsforauthorsdatesandcomments} shows how the \code{ScoreFunction} can be adapted to extract authors, dates and comments.

@@

Properties \ref{wordorderProp} and \ref{lengthProp} are essential when dealing with cases where the blog's web feed only contains an abstract or a subset of the entire post article. \autoref{similarityTable} gives examples to illustrate how these two properties hold for the Sørensen–Dice coefficient similarity but do not for \emph{edit distance} based similarities such as the Levenshtein \cite{levenshtein1966} similarity.
